Fivebranes

### 2022-02-22 fivebranes/index.tex
edit

We begin by using the twisted holography proposal to compute an index counting local operators of the holomorphic twist of the theory on a large number of M5 branes. Let us briefly recall the proposal specialized to our situation \surya{more elaboration elsewhere}. Let $\cL$ denote the local $L_{\infty}$ algebra underlying the minimal twist of 11 dimensional supergravity on $\R_{t}\times \C^{3}_{z_{i}}\times \C^{2}_{w_{a}}$. Consider a stack of $N$ M5 branes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\iota : \{0\}\times \C^{3} \times \{0\}\to \R\times \C^{5}$ denote the inclusion of their support. The twisted holography proposal asserts that the algebra of local operators of the minimally twisted M5 brane theory in the large $N$ limit is a deformation of the factorization envelope $\cU(\iota^{*} \cL) = C_{\bullet}\left ((\iota^{*}\cL)_{c} \right )$.

Since quantities like indices are deformation invariants, we need not consider such deformations for now. In fact we may replace $\cL$ with the abelian local dg Lie algebra describing the free limit. Explicitly, $\cL$ is given by the following sheaf of $\Z/2$-graded cochain complexes

\[
\begin{tikzcd}
  &  \ul{\rm even} & \ul{\rm odd} \\
 \mu \in & \Omega^{\bullet}_{\R}\otimes\PV^{1,\bullet}_{C^{5}} \ar[r, "\del_{\Omega}"] & \Omega^{\bullet}_{\R}\otimes\PV^{0,\bullet}_{\C^{5}}\\
 \gamma \in & \Omega^{\bullet}_{\R}\otimes\Omega^{0,\bullet}_{\C^{5}} \ar[r, "\del"]
& \Omega^{\bullet}_{\R}\otimes\Omega^{1,\bullet}_{\C^{5}}\end{tikzcd}
.\]

\parsec
We begin by computing the hypercohomology of the factorization envelope. Strictly speaking, this is not necessary for computing the index, but will be useful in later calculations.

@@

\begin{lem}
  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}(\C^{3}_{z}, \c U (\iota^{*}cL))\Sym (V_{\gamma}\oplus \Pi V_{\mu})\] where
  \begin{itemize}
    \item $V_{\gamma}$ is spanned by
          \begin{align}
            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}dz_{1} \\
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{2}, \ \ \
             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{3} \\
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{1}, \ \ \
            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{2}
          \end{align}

>>>>

We begin by using the twisted holography proposal to compute an index counting local operators of the holomorphic twist of the theory on a large number of M5 branes. Let us briefly recall the proposal specialized to our situation \surya{more elaboration elsewhere}. Let $\cL$ denote the local $L_{\infty}$ algebra underlying the minimal twist of 11 dimensional supergravity on $\R_{t}\times \C^{3}_{z_{i}}\times \C^{2}_{w_{a}}$. Consider a stack of $N$ M5 branes supported at the origin in $\R\times \C^{2}_{w_{a}}$ and let $\iota : \{0\}\times \C^{3} \times \{0\}\to \R\times \C^{5}$ denote the inclusion of their support. The twisted holography proposal asserts that the algebra of local operators of the minimally twisted M5 brane theory in the large $N$ limit is a deformation of the factorization enveloping algebra 
\[
\bU(\iota^{*} \cL) = C_{\bullet}\left( (\iota^{*}\cL)_{c} \right) .
\]

Since quantities like indices are deformation invariant, we need not consider such deformations for now. 
In fact in this section we may, and will, replace the local Lie algebra $\cL$ with the abelian local dg Lie algebra which underlies the free limit of the twisted supergravity theory. 
Explicitly, $\cL$ is given by the following sheaf of $\Z/2$-graded cochain complexes
\[
\begin{tikzcd}
  &  \ul{\rm even} & \ul{\rm odd} \\
 \mu \in & \Omega^{\bullet}_{\R}\otimes\PV^{1,\bullet}_{\C^{5}} \ar[r, "\del_{\Omega}"] & \Omega^{\bullet}_{\R}\otimes\PV^{0,\bullet}_{\C^{5}}\\
 \gamma \in & \Omega^{\bullet}_{\R}\otimes\Omega^{0,\bullet}_{\C^{5}} \ar[r, "\del"]
& \Omega^{\bullet}_{\R}\otimes\Omega^{1,\bullet}_{\C^{5}}\end{tikzcd}
.\]

\parsec

Let us describe the restriction $\iota^* \cL$ along the inclusion of the brane.
The $\mu$-field decomposes into vector field components which point along and transverse to the brane
\[
\mu
\]
%
%is the sheaf of $\Z/2$-graded cochain complexes
%\[
%\begin{tikzcd}
%  &  \ul{\rm even} & \ul{\rm odd} \\
% \mu|_{w=t=0} \in & \PV^{1,\bullet}_{\C^{3}} \ar[r, "\del_{\Omega}"] & \PV^{0,\bullet}_{\C^{3}}\\
% \gamma|_{w=t=0} \in & \Omega^{0,\bullet}_{\C^{3}} \ar[r, "\del"]
%& \Omega^{1,\bullet}_{\C^{3}}\end{tikzcd}
%.\]

We begin by computing the hypercohomology of the factorization enveloping algebra. Strictly speaking, this is not necessary for computing the index, but will be useful in later calculations.

@@

\begin{lem}
  As $\Z/2$-graded vector spaces, we have that \[H^{\bu}(\C^{3}_{z}, \cU (\iota^{*}cL))\Sym (V_{\gamma}\oplus \Pi V_{\mu})\] where
  \begin{itemize}
    \item $V_{\gamma}$ is spanned by
          \begin{align}
            & \delta^{(0,b,c)}w_{1}^{k}w_{2}^{l}dz_{1} \\
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{2}, \ \ \
             \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dz_{3} \\
            & \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{1}, \ \ \
            \delta^{(a,b,c)}w_{1}^{k}w_{2}^{l}dw_{2}
          \end{align}
